### 2024-07-19 options/symbols_and_cmd.tex
(Almost) all comments from FC on atom_molecules review
Still have to implement the one about the graphs on UQ and parameters of molecules and SMR
Rebuttals: Keep going...
First version of rebuttals completed + Grammarly Intro + Chap. 1 & 2
Grammarly up to 4.2 (included)

%% B
\newabbreviation[group={Acronyms}]{BECCS}{BECCS}{Bioenergy with Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{BEMS}{BEMS}{Building Energy Management System}
\newabbreviation[group={Acronyms}]{BEV}{BEV}{Battery Electric Vehicle}
\newabbreviation[group={Acronyms}]{BTX}{BTX}{Benzene, Toluene and Xylene}

@@

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{Energy System Optimisation Models}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{End-Use Demand}

@@

%% P
\newabbreviation[group={Acronyms}]{PC}{PC}{Principal Component}
\newabbreviation[group={Acronyms}]{PCs}{PCs}{Principal Components}
\newabbreviation[group={Acronyms}]{PCA}{PCA}{Principal Component Analysis}
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PDF}{PDF}{Probability Density Function}
\newabbreviation[group={Acronyms}]{PV}{PV}{Photovoltaic}

@@

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor Critic}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{Small Modular Reactor}
\newabbreviation[group={Acronyms}]{SVD}{SVD}{Singular Value Decomposition}

>>>>

%% B
\newabbreviation[group={Acronyms}]{BECCS}{BECCS}{Bioenergy with Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{BEMS}{BEMS}{Building Energy Management System}
\newabbreviation[group={Acronyms}]{BEV}{BEV}{Battery Electric Vehicles}
\newabbreviation[group={Acronyms}]{BTX}{BTX}{Benzene, Toluene and Xylene}

@@

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{Energy System Optimisation Models}
\newabbreviation[group={Acronyms}]{ESTD}{ESTD}{EnergyScope Typical Days}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{End-Use Demand}

@@

%% P
\newabbreviation[group={Acronyms}]{PC}{PC}{Principal Component}
\newabbreviation[group={Acronyms}]{PCs}{PCs}{Principal Components}
\newabbreviation[group={Acronyms}]{PCA}{PCA}{Principal Component Analysis}
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PV}{PV}{Photovoltaic}

@@

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor-Critic}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{Small Modular Reactor}
\newabbreviation[group={Acronyms}]{SVD}{SVD}{Singular Value Decomposition}
